Some usefull words/expressions/sentences

### 2018-06-27 phrases.Rmd
foundamentalpart read 30%

@@

>>>>

- daunting ['dɔ:ntiŋ]

```
======= 辞典翻译: daunting =======
adj. 使人畏缩的；使人气馁的；令人怯步的
============ 网络释义 ============
---------- Daunting ----------
令人生畏
使人畏缩的
使人气馁的
------ However Daunting ------
但艰巨
--------- B daunting ---------
使胆怯
```

- discern [di'sə:n, -'zə:n]

```
======= 辞典翻译: discern ========
  vt. 识别；领悟，认识
  vi. 看清楚，辨别
============ 网络释义 ============
---------- discern -----------
  看出
  辨别
  识别
-------- Discern Lies --------
  辨知谎言
  辨识谎言
  洞悉谎言
------- discern safely -------
  安全识别
```

@@

#### collins2010latent - Latent Class and Latent Transition Analysis: With Applications in the Social, Behavioral, and Health Sciences

- It is particularly noteworthy that the causal flow is *from* the latent variable *to* the indicator variable, not the other way around. That is, observed indicator variables do not cause the latent variables.

- The purpose of LCA is to help the investigator to discern any meaningful, scientifically interesting classes against the noisy background of error.

- In LCA, it is the responsibility of the investigator to assign names to the latent classes.

- The starting point for conducting a latent class analysis on empirical data is a contingency table formed by cross-tabulating all the observed variables to be involved in the analysis.
